The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-13 analysis/paper/paper.qmd
Add small corrections under data collection

## Data

@@

Both the raw and cleaned data are published in the 4TU.ResearchData repository \[ADD CITATION\].

@@

## Data analysis

### Pre-processing

@@

# Add cleaned text column with removed stop words
emu$text_clean <- emu$text_clean |>
  str_remove_all(find_meta_stopwords(emu)) |> 
  str_remove_all(urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism", "tu delft", "ku leuven", "upcs barcelona", "iuav venice", 
                      "space", "spatial", "spaces", "plan", "public", "development"))) |>
  str_remove_all(thesis_stopwords(add_stopwords = c("advisor", "prof", "fig", "ure", "ning")))

>>>>

## Data collection

@@

Both the raw and cleaned data are published in the 4TU.ResearchData repository [ADD CITATION].

@@

## Pre-processing

@@

# TODO replace with cleaning steps including ngram concatenation
# Add cleaned text column with removed stop words
emu$text_clean <- emu$text_clean |>
  str_remove_all(find_meta_stopwords(emu)) |> 
  str_remove_all(urbanism_stopwords(
    add_stopwords = c("emu", "european postgraduate master in urbanism", "tu delft", "ku leuven", "upcs barcelona", "iuav venice", 
                      "space", "spatial", "spaces", "plan", "public", "development"))) |>
  str_remove_all(thesis_stopwords(add_stopwords = c("advisor", "prof", "fig", "ure", "ning")))
